---
Title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and clean data

1.Show any code that is needed to

Load the data (i.e. \color{red}{\verb|read.csv()|}read.csv())
Process/transform the data (if necessary) into a format suitable for your analysis

```{r}
getwd()

```
```{r}
 setwd('C:/Users/Administrator/Desktop/Coursera data science specification/Course 4 Exploratory data analysis/Project wk2/RepData_PeerAssessment1')

```

2.Loading the data

```{r}
Act<- read.csv("activity.csv")

```


Checking the data

```{r}
dim(Act)

```
3.Clean data without NA value
```{r}
cleanAct <- Act[ with (Act, { !(is.na(steps)) } ), ]
```
```{r}
dim(cleanAct)
str(cleanAct)
Head(cleanAct)
```
## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
